\section{Introduction}

Simulation plays an important role in particle and nuclear physics. It is widely used in detecor design and to compare experimental data to theoretical models. Traditionally, simulation relies on \textit{Monte Carlo methods} and requires significant computational resources. Such methods does not not scale to meet the growing demands resulting from large quantities of data expected during High Luminosity Large Hadron Collider (HL LHC) runs. The detailed simulation of particle collisions and interactions as captured by detectors at the LHC using a well known simulation software \geant annually requires billions of CPU hours constituting more than half of the LHC experiments' computing resources \cite{bozzi2014, flynn2015computing}. More specifically, the detailed simulation of particle showers in calorimeters is the most computationally demanding step.
 
A line of simulation methods exploit the idea of reusing previously calculated or measured physical quantities have been developed to reduce the computation time \cite{grindhammer2000parameterized,atlas2010simulation}. These approach suffers from being specific to an individual experiment and, despite being faster than the full simulation, they still take relatively long to apply. Thus, the particle physics community is in need of new faster simulation methods to model experiments. 
    
One of the possible approaches to simulate the calorimeter response is using the \textit{deep learning} techniques. In particular, a recent work, CaloGAN \cite{paganini2017calogan}, provided an evidence that \textit{Generative Adversarial Networks} can be used to efficiently simulate particle showers. While they achieved over $100,000 \times$ speed-up over \geant, their setup was quite simple as they parametrized an input particle only by its energy. Moreover, the quality of their simulation is unsatisfactory \todo{Fedor, is it true?}. 

In this work we build a model upon \text{Wasserstein Generative Advesarial Networks} and show its superior performance over CaloGAN. We also evaluate our model in a more complex scenario, when a particle is described by $5$ parameters: 3d momentum $(p_x,~ p_y,~ p_z)$ and 2d coordinate $(x,~ y)$. Our method for high-fidelity fast simulation of particle showers in the specific LHCb calorimeter aims to replace the existing Monte Carlo based methods and achieve a significant speed-up factor.
 

% Our contirubtion is three fold: 

% \begin{itemize}
%     \item We build and extensively evaluate a simupropose a  
%     \item 
%     \item Dataset? 
% \end{itemize}

